Derivation Write Up

### 2020-05-20 ChaoticDynamics/WriteUp.tex
Complete Chapter 8 on Swarm Control

\usepackage[margin=2cm]{geometry}

@@

	\begin{itemize}
		\item Focuses on stateless games
		\item Homogeneous agents
		\item Discrete action spaces
		\item Small, finite number of agents.
	\end{itemize}

@@

>>>>

\usepackage[margin=2cm]{geometry}
\usepackage{amsmath}

@@

	\begin{itemize}
		\item Focuses on stateless games
		\item Homogeneous agents
		\item Discrete action spaces, with large number of actions.
		\item Small, finite number of agents.
	\end{itemize}

@@

	\section{Derivation} % (fold)
	\label{sec:derivation}

	We start with the two-agent Q-Learning dynamics as presented by Tuyls et al.

	\begin{subequations}
		\begin{equation}
			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
		\end{equation}
		\begin{equation}
			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i})
		\end{equation}
	\end{subequations}

	In order to follow the conventions of spin glass theory for the analysis of disordered systems,
	we rescale the system so that the payoff matrix elements are of order $N^{-1/2}$. The motivation
	for doing this is that, along the way, we will take the limit of the number of actions $N$ to
	infinity. However, doing this will result in numerical underflow of the action probabilities 
	(i.e. the probability of each action goes to zero). To compensate for this, we adjust the
	system so that the sum of the probabilities add to $N$. The scaling goes as follows:

	\begin{subequations*}
		\begin{equation*}
			a_{ij} = \sqrt{N} \tilde{a_{ij}}
		\end{equation*}
		\begin{equation*}
			b_{ji} = \sqrt{N} \tilde{b_{ji}}
		\end{equation*}
	\end{subequations*}

	We compensate for this change with
	\begin{subequations*}
		\begin{equation*}
			x_{i} = \tilde{x_{i}}/N
		\end{equation*}
		\begin{equation*}
			y_{i} = \tilde{y_i}/N
		\end{equation*}
	\end{subequations*}

	This gives the original equations as

	\begin{subequations}
		\begin{equation}
			\frac{\dot{\tilde{x_i}}(t)}{\tilde{x_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{a_
			{ij}} 
			\tilde{y_j} -
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{x_i} \tilde{a_{ij}} \tilde{y_j}
			+ \tilde{\alpha} \sum_j \tilde{x_j} ln(\frac{\tilde{x_j}}{\tilde{x_i}}) 
		\end{equation}
		\begin{equation}
			\frac{\dot{\tilde{y_i}}(t)}{\tilde{y_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{b_
			{ij}} 
			\tilde{x_j} -
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{y_i} \tilde{b_{ij}} \tilde{x_j}
			+ \tilde{\alpha} \sum_j \tilde{y_j} ln(\frac{\tilde{y_j}}{\tilde{y_i}}) 
		\end{equation}
	\end{subequations}

	% section derivation (end)
